---
title: "GrazingCurveFits_LiveCode"
author: "HVM"
date: "4/18/2023"
output: html_document
---

```{r}
extrdat <- read.csv("/Users/hollyvm/GoogleSync/Collaborations/MVCOCiliates/CiliateGrazingData - ExtractedData.csv",header=T)
head(extrdat)
str(extrdat) # str() = structure
```


```{r}
extrdat$Pred.Prey <- paste(extrdat$Genus,extrdat$Species,'.',extrdat$Prey,sep='')

Pred.Prey.list <- unique(extrdat$Pred.Prey)
length(Pred.Prey.list)

```

```{r}
Pred.Prey.list[1]
subdat <- extrdat[extrdat$Pred.Prey==Pred.Prey.list[1],]
dim(subdat)
subdat <- subdat[!is.na(subdat$PreyConsumption.preyperciliateperday),]
dim(subdat)

head(subdat)

```

This is basic text...

```{r,fig.width=3,fig.height=2}
plot(subdat$PreyConc.cellsmL,subdat$PreyConsumption.preyperciliateperday,las=1,xlab='Prey Concentration (cells/mL)',ylab='Consumption Rate (prey per ciliate per day)')

subdat2 <- subdat[subdat$Light.Level==100&subdat$Salinity==35,]

plot(subdat2$PreyConc.cellsmL,subdat2$PreyConsumption.preyperciliateperday,las=1,xlab='Prey Concentration (cells/mL)',ylab='Consumption Rate (prey per ciliate per day)')
```

Let's use nls() to fit a saturating curve shape

```{r}
help(nls)
```

Holling Type II Functional Response:

$$
g = \frac{aP}{1+ahP}
$$


```{r}

nls(PreyConsumption.preyperciliateperday ~ a*PreyConc.cellsmL/(1+a*h*PreyConc.cellsmL) , data = subdat, start = list(a = 1/2000 , h = 1/4))



```

```{r,fig.width=3,fig.height=2}
plot(subdat$PreyConc.cellsmL,subdat$PreyConsumption.preyperciliateperday,las=1,xlab='Prey Concentration (cells/mL)',ylab='Consumption Rate (prey per ciliate per day)')

Prey.set <- seq(from=0,to=max(subdat$PreyConc.cellsmL),length.out = 1000)
Predictions <- 0.002132*Prey.set/(1+0.002132*0.305760*Prey.set)

lines(Prey.set,Predictions,lwd=2,col='blue')

```

Fancier approach!

Step one: Estimate the starting parameter values

```{r}
# Estimate the attack rate as the slope of the data
a.est <- lm(subdat$PreyConsumption.preyperciliateperday~subdat$PreyConc.cellsmL)$coefficients[2]

# Estimate the handling time as 1/max grazing rate
h.est <- 1/max(subdat$PreyConsumption.preyperciliateperday)


```


Step two: Fit the model

```{r}

fit1 <- nls(PreyConsumption.preyperciliateperday ~ a*PreyConc.cellsmL/(1+a*h*PreyConc.cellsmL) , data = subdat, start = list(a = a.est , h = h.est))

fit1

summary(fit1)

a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]
```

Step three: overlay fit on the plot

```{r,fig.width=3,fig.height=2}
plot(subdat$PreyConc.cellsmL,subdat$PreyConsumption.preyperciliateperday,las=1,xlab='Prey Concentration (cells/mL)',ylab='Consumption Rate (prey per ciliate per day)')

Prey.set <- seq(from=0,to=max(subdat$PreyConc.cellsmL),length.out = 1000)
Predictions <- a.fit*Prey.set/(1+a.fit*h.fit*Prey.set)

lines(Prey.set,Predictions,lwd=2,col='blue')

```


# Subheader: Growth
## Subsubheader
### can i do three?

Monod kinetics (for growth) with an x-intercept representing the minimum amount of prey for positive growth.

$$
\mu = \frac{\mu_{\max}(P-x)}{H+(P-x)}
$$



